\documentclass{book}
\usepackage{import}

\title{Codex Master of PhaseIR}
\author{Edward X. Meisner}
\date{\today}

\begin{document}
\maketitle

\chapter*{Preface}
\begin{flushright}
\textit{“Every chronicity finds its glyph in phase.”} \\
— Vigrahaksetra Codex
\end{flushright}

This master Codex binds together the mythic commentaries and technical operators 
of all domains. Each local Codex remains modular, but here they are woven into 
a single lineage.

\chapter{PhaseIR Overview}
\section*{Bridge}
PhaseIR is the blueprinting chamber where all chronicities of time are transduced 
into phase. This overview sets the stage for the domain Codices that follow.

\section{Design Principles}
- Modularity: each domain has its own Codex.
- Dual Layering: technical operators + mythic commentary.
- Universality: all chronicities converge into quasi‑universal phase cells.
- Extensibility: new domains can be added seamlessly.

% === Domain Imports ===
\chapter{Elliptic Time}
\import{phaseIR/elliptic/}{Codex.tex}

\chapter{Fractal Time}
\import{phaseIR/fractal/}{Codex.tex}

\chapter{Spectral Time}
\import{phaseIR/spectral/}{Codex.tex}

\chapter{Thermodynamic \& Wick Time}
\import{phaseIR/thermo/}{Codex.tex}

\chapter{p-Adic Time}
\import{phaseIR/pAdic/}{Codex.tex}

\chapter*{Epilogue}
\begin{flushright}
\textit{“The lineage is not closed; each operator is a door.”}
\end{flushright}

The Codex Master does not end the mythos — it ensures continuity, 
so that future domains may be grafted into the lineage without rupture.

\end{document}
